\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\title{Two-Experiment Plan: $\sigma$-Uniform vs. $\tau$-Uniform Metrology in QFT}
\author{Protocol Addendum to LTQG}
\date{\today}
\begin{document}
\maketitle

\section*{Principle}
Observables are invariant under monotone reparameterizations of time, but \emph{measurement protocols} need not be.
Uniform sampling in $\sigma=\log(\tau/\tau_0)$ redistributes resolution towards early proper times.
We propose two numerically reproducible experiments with acceptance criteria.

\section{Experiment A: Bogoliubov Coefficients in Expanding FLRW}
\paragraph{Model.}
Real scalar field on spatially flat FLRW with $a(\tau)= (\tau/\tau_*)^p$, $p\in\{\tfrac12,\tfrac23\}$.
Use canonical variable $v=a^{3/2}u$ with mode equation
\begin{equation}
 v_k'' + \omega_k(\tau)^2 v_k = 0,\qquad \omega_k^2 = k^2 a^{-2} + m^2 - \frac{a''}{a} - \frac{3}{2}\left(\frac{a'}{a}\right)^{\!\!2},
\end{equation}
primes denoting $\tau$-derivatives.
Impose $W[v_k,\bar v_k]=i$ at a shared early-time slice.

\paragraph{Protocol.}
Integrate modes over a fixed physical interval in the scale factor (e.g.\ $a\in[a_i,a_f]$).
Construct instantaneous adiabatic vacuum and extract $(\alpha_k,\beta_k)$ via the KG inner product on common slices.
Repeat with sampling grids:
(i) $N$ samples uniform in $\tau$, (ii) $N$ samples uniform in $\sigma$.

\paragraph{Hypothesis.}
$\beta_k$ estimates converge to the same continuum limit, but \emph{$\sigma$-uniform sampling reduces bias/variance} at fixed $N$ for spectra with early-time structure.

\paragraph{Acceptance criteria.}
For $k$ in a fixed decade and $N$ fixed,
\begin{align}
 \max_k \left|\ |\beta_k|^2_{\tau\text{-grid}} - |\beta_k|^2_{\sigma\text{-grid}}\right| &\le \varepsilon_1(N),\\
 \text{MSE}_\sigma(N) &< \text{MSE}_\tau(N) \quad \text{by a factor }\ge 1+\delta,
\end{align}
with typical targets $\varepsilon_1\sim 10^{-6}$, $\delta\sim 0.2$.

\section{Experiment B: Near-Horizon Phase Accumulation (Unruh--DeWitt Detector)}
\paragraph{Model.}
Static Schwarzschild exterior with detector on a stationary worldline at areal radius $r>r_s$.
Proper time increment is $d\tau = \sqrt{1-r_s/r}\, dt$.
Consider a detector with switching function $\chi(\cdot)$ and energy gap $\Omega$; the response function is
\begin{equation}
 \mathcal{F} \propto \int d\tau\, d\tau'\, \chi(\tau)\chi(\tau') e^{-i\Omega(\tau-\tau')} W(\tau,\tau'),
\end{equation}
with $W$ the pullback of the Wightman function.

\paragraph{Protocol.}
Compare two families of compactly supported switching functions of equal $L^1$-mass:
(i) Uniform windows in $\tau$ of width $\Delta\tau$;
(ii) Uniform windows in $\sigma=\log(\tau/\tau_0)$ mapped back to $\tau$ with Jacobian $d\tau=\tau\,d\sigma$ (thus earlier $\tau$ receive finer weight).
Evaluate $\mathcal{F}$ numerically (or via near-horizon Rindler approximation).

\paragraph{Hypothesis.}
For windows that extend towards smaller $\tau$ (closer to the horizon or early-time segments), the $\sigma$-uniform protocol \emph{stabilizes} phase accumulation and exhibits reduced sensitivity to ultraviolet transients, consistent with the ``asymptotic silence'' scaling.

\paragraph{Acceptance criteria.}
For matching support endpoints,
\begin{align}
 |\mathcal{F}_\sigma - \mathcal{F}_\tau| &\le \varepsilon_2 \quad (\text{invariance}),\\
 \mathrm{Var}[\mathcal{F}_\sigma] &< \mathrm{Var}[\mathcal{F}_\tau] \quad \text{over grid refinements, by }\ge 1+\delta.
\end{align}

\section{Reproducibility Notes}
\begin{itemize}
 \item Use shared random seeds and identical physical slices for comparisons.
 \item Track Wronskian drift and KG norm as sanity checks: target $\le 10^{-8}$.
 \item Publish code and config files; report $(N, \text{grid type})$ and wall-clock, to quantify efficiency gains from $\sigma$-uniform sampling.
\end{itemize}

\end{document}